Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond

### 2024-02-08 birthrate.qmd
Update birthrate.qmd

## Source

>>>>

## Source
### Trend in US Birth Rates

# Load necessary libraries
library(ggplot2)

# Read the data from CSV file
data <- read.csv("fig_1.csv")

# Plotting the data
ggplot(data, aes(x = year, y = brate_all)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 2007, linetype = "dotted") +
  labs(x = "Year", y = "Births per 1,000 women age 15-44",
       title = "Birth Rates per 1,000 Women Age 15-44 Over Time",
       subtitle = "Source: CDC Vital Statistics Births Reports (2015, 2019, 2020)",
       caption = "Trend in US Birth Rates") +
  theme_minimal()
